\documentclass[../cv_xin.tex]{subfiles}

%\bibliography{../local.bib,../patents_misc.bib}
%\addbibresource{../local.bib}
%\addbibresource{../patents_misc.bib}
\begin{document}
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Technical Director} % Job title
    {Newrizon} % Organization
    {Shanghai, China} % Location
    {Nov. 2020 - May 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
          \item Reinforcemnt learning based electric powertrain control optimization in multimodal complex environments
          \hyperlink{Xin_VEOS_22}{$\rightarrow$\circled{P}7} \hyperlink{Xin_Fu_Pan_Simulation_Test_RL_22}{\circled{P}8} \hyperlink{Pan_Xin_DrvStyle_23}{\circled{P}3}.
          \item Time series anomaly detection and battery state of safety prediction based on generative models. \hyperlink{Xin_GenAI_23}{$\rightarrow$\circled{P}5} \hyperlink{Xin_Chen_NN_TSFeatures_23}{\circled{P}6}
          \item Application of multimodal foundation model and large language model in autonomous driving \hyperlink{Xin_LLM_24}{\circled{P}1} \hyperlink{Xin_VLM_24}{\circled{P}2} \hyperlink{Xin_Latent_Diffusion_23}{\circled{P}4}.
          \item Software design \& development of streaming data pipeline for time sequence:
            \begin{itemize}
                    \item Online deep reinforcement learning data pipeline (ETL, Deep Learning Training/Inference pipelines) \href{https://binjian.github.io/tspace/}{$\rightarrow$ \textbf{tspace}},
                    \item CAN Application package \href{https://binjian.github.io/candycan/}{$\rightarrow$ \textbf{candycan}},
                    \item Time series analysis with generative AI \href{https://github.io/binjian/funes-ts/}{$\rightarrow$ \textbf{funes-ts}}.
                    %\item \href{https://binjian.gitlab.io/tspace/}{tspace}
            \end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Manager} % Job title
    {Nio} % Organization
    {Shanghai, China} % Location
    {Nov. 2017 - Nov. 2020} % Date(s)
    {
      \begin{cvitems}
        \item Advanced hardware and software design of L4 autonomous driving system.
        \item Team (10+ engineers) build-up and development management.
        \item Fleet: electric vehicles (10+) with level 4 sensor configuration and computing platform.
        \item Intelligent charging and automatic parking assistance system (public funded project).
        \item License application and operation of Intelligent Connected Vehicle (ICV) road test in Shanghai and Beijing.
        \item Top 3 at testing mileage in Beijing with T3 license.
        \item 5G ICV Demonstration in Hainan Boao Forum, 2019.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Technical Manager} % Job title
    {Patac/SAIC-GM} % Organization
    {Shanghai, China} % Location
    {Oct. 2015 - Nov. 2017} % Date(s)
    {
      \begin{cvitems}
        \item System \& software architecture design for active safety domain unit (ADU).
        \item PATAC ADU A sample: system and software architecture of embedded platform.
        \item Software architecture of SAIC-MAXUS SV73 highway assist.
        \item Camera based driver monitoring system.
        \item Surround view camera system \hyperlink{Xin_RearView_17}{\circled{P}9}.
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Software Manager} % Job title
    {Visteon Asian Pacific} % Organization
    {Shanghai, China} % Location
    {Jan. 2015 - Aug. 2015} % Date(s)
    {
      \begin{cvitems}
        \item SOP project of instrument clusters.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Manager} % Job title
    {Hella Shanghai Electronics} % Organization
    {Shanghai, China} % Location
    {Jul. 2014 - Jan. 2015} % Date(s)
    {
      \begin{cvitems}
        \item SOP project of BCM and PEPS.
        \item Platform project of PEPS, BCM, BSW.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Manager} % Job title
    {Harman Shanghai R\&D Center} % Organization
    {Shanghai, China} % Location
    {Sep. 2009 - Jul. 2014} % Date(s)
    {
      \begin{cvitems}
        \item Development of video based ADAS system.
        \item SOP projects of camera based parking systems:
          \begin{itemize}
            \item SOP of 3D surround view system (SVS) for Geely KC-1,
            \item SOP of rear view camera deployment (Geely, Ssangyong, Tata, GM, Suzuki, Hyundai and VW),
            \item Fusion with ultrasonic parking assistance.
           \end{itemize}
        \item Supervision of ADAS advanced research:
          \begin{itemize}
            \item LDW and FCW on infotainment platform,
            \item Augmented navigation,
            \item Moving object detection.
            \item Design of surround view demo systems (Robot car and OEM vehicles) and demos (CES, Geneva Motor Show).
          \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
\end{document}
