\documentclass[../cv.tex]{subfiles}

%\bibliography{../local.bib,../patents_misc.bib}
%\addbibresource{../local.bib}
%\addbibresource{../patents_misc.bib}
\begin{document}
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

	%---------------------------------------------------------
	\cventry
	{Technical Expert, Advanced Development} % Job title
	{Newrizon} % Organization
	{Shanghai, China} % Location
	{Nov. 2020 - May 2024} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item Reinforcemnt learning based motion planning (~20\% increase in energy efficiency)
			\supercite{Xin_VEOS_22} \supercite{Xin_Fu_Pan_Simulation_Test_RL_22} \supercite{Pan_Xin_DrvStyle_23}.
			\begin{itemize}
				\item Application of DDPG, TD3, SAC in Online/Offline mode for motion planning
				\item Sequential model based reinforcement learning (RDPG)  for POMDP
				\item Distributed training of multi-agent and federated learning
				\item Diffusion based Q-Learning (IDQL) for offline reinforcement learning
				\item Design and implementation of deep reinforcement learning data pipeline (ETL \& Deep Learning)
				      $\rightarrow$ \textbf{tspace} \href{https://binjian.github.io/tspace/}{\faGithub}
				\item CAN Application package (Pydantic integration, CI/CD with Github Action, dynamic loading, property cache)
				      $\rightarrow$ \textbf{candycan} \href{https://binjian.github.io/candycan/}{\faGithub}
			\end{itemize}
			\item Deep learning based time series prediction and battery state of safety prediction based on generative models. \supercite{Xin_GenAI_23} \supercite{Xin_Chen_NN_TSFeatures_23}
			\begin{itemize}
				\item Unsupervised learning of multimodal time series with GANs
				\item Design and implementation of time series analysis software package with generative models
				      $\rightarrow$ \textbf{funes-ts} \href{https://github.com/binjian/funes-ts/}{\faGithub}
				\item Prediction based on time series foundation model
				\item Model distillation and data distillation
			\end{itemize}
			\item Research in applications of end-to-end perception and planning in autonomous driving.
			\begin{itemize}
				\item Driving decision of automated driving systems with natural languange interface based on LLMs or VLMs \supercite{Xin_LLM_24}  \supercite{Xin_VLM_24}
				\item Occlusion recovery with latent diffusion models for front-view camera \supercite{Xin_Latent_Diffusion_23}
				\item 3D reconstruction of driving scenes with NERF and Gaussian Splatting
				\item Neural motion planning (MPNet)
				\item Behavior and motion prediction (CVAE-H, VectorNet, TNT, Trajectron++, MotionDiffuser)
				\item Driving style adaption for autonomous driving (DAgger/RLHF/DPO/ControlNet in MetaDrive)
				\item Model-based reinforcement learning (World Model,Dreamer,APRL)
				\item Diffusion policy for reinforcement learning (Quality Score Matching, Diffusion Policy)
			\end{itemize}
			\item Chip evaluation (Chiplite Chiplet SoC on self-driving applications)
			\item Team 2 engineers
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Senior Manager, Autonomous Driving} % Job title
	{Nio} % Organization
	{Shanghai, China} % Location
	{Nov. 2017 - Nov. 2020} % Date(s)
	{
		\begin{cvitems}
			\item Development of L4 autonomous driving systems.
			  \begin{itemize}
			    \item perception and sensor fusion
				  \begin{itemize}
					\item Image object detection and semantic segmentation (Darknet)
					\item Traffic light detection and its state estimation
					\item Lidar point cloud processing and object detection (pointnet++)
					\item Monocular depth (based on calibration,vanishing point estimation, monocular depth with Packnet-SFM)
				  	\item Radar, Video and lidar object sensor fusion and object tracking
					\item Radar signal processing and data fusion with MHA or JPDA
					\item Camera, Lidar calibration
				  \end{itemize}
			    \item Motion planning and vehicle control
				  \begin{itemize}
				  	\item Routing with dynamic programming (Hybrid A*,RRT,MCTS)
					\item APA routing with Reeds-Shepp constraints
					\item Path planning with MPC
					\item behavior planning with vehicle state machine
					\item Behvior cloning of lateral planning based on recurrent models
				  \end{itemize}
				\item ADS system development and integration under ROS
			\end{itemize}
			\item Fleet: electric vehicles (10+) with level 4 sensor configuration and computing platform.
			\item Intelligent charging and automatic parking assistance system (public funded project).
			\item License application and operation of Intelligent Connected Vehicle (ICV) road test in Shanghai and Beijing.
			\item Top 3 at testing mileage in Beijing with T3 license.
			\item 5G ICV Demonstration in Hainan Boao Forum, 2019.
			\item Chip evaluation (Huawei Ascend on self-driving applications)
			\item Team (10+ engineers) build-up and development management.
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Technical Manager, ADAS} % Job title
	{Patac/SAIC-GM} % Organization
	{Shanghai, China} % Location
	{Oct. 2015 - Nov. 2017} % Date(s)
	{
		\begin{cvitems}
			\item System \& software architecture design for active safety domain unit (ADU).
			\item PATAC ADU A sample: system and software architecture of embedded platform.
			\item Software architecture of SAIC-MAXUS SV73 highway assist.
			\item Camera based driver monitoring system.
			\item Surround view camera system \supercite{Xin_RearView_17}.
			\item Team 3 engineers
		\end{cvitems}
	}


	%---------------------------------------------------------
	\cventry
	{Software Manager} % Job title
	{Visteon Asia Pacific} % Organization
	{Shanghai, China} % Location
	{Jan. 2015 - Aug. 2015} % Date(s)
	{
		\begin{cvitems}
			\item SOP project of instrument clusters.
			\item Team 15+ engineers
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Senior Manager, Software} % Job title
	{Hella Electronics} % Organization
	{Shanghai, China} % Location
	{Jul. 2014 - Jan. 2015} % Date(s)
	{
		\begin{cvitems}
			\item SOP project of BCM and PEPS.
			\item Platform project of PEPS, BCM, BSW.
			\item Team 15+ engineers
		\end{cvitems}
	}

	%---------------------------------------------------------
	\cventry
	{Senior Manager, ADAS} % Job title
	{Harman R\&D Center} % Organization
	{Shanghai, China} % Location
	{Sep. 2009 - Jul. 2014} % Date(s)
	{
		\begin{cvitems}
			\item Development of video based ADAS system.
			\item SOP projects of camera based parking systems
			\begin{itemize}
				\item SOP of 3D surround view system (SVS) for Geely KC-1, first SOP of SVS in China
				\item SOP of rear view camera deployment (Geely, Ssangyong, Tata, GM, Suzuki, Hyundai and VW).
			\end{itemize}
			\item Supervision of ADAS advanced research:
			\begin{itemize}
				\item LDW and FCW on infotainment platform,
				\item Augmented navigation,
				\item Moving object detection.
				\item Design of surround view demo systems (Robot car and OEM vehicles) and demos (CES, Geneva Motor Show).
			\end{itemize}
			\item Team ~10 engineers
		\end{cvitems}
	}
	%---------------------------------------------------------
\end{cventries}
\end{document}
